---
title: "Penguin Analysis: R and Python Together"
author: "Anuoluwapo Akinkunmi"
date: 2026-09-25
---

Data: [palmerpenguins](https://allisonhorst.github.io/palmerpenguins/),
Palmer Station Antarctica LTER (CC0 licence).

This post computes a summary in R, passes it to Python for a
calculation, then passes that result back to R for a plot.

```{r}
#| message: false
#| warning: false
library(reticulate)
library(here)
reticulate::use_python(here::here(".venv", "bin", "python")
, required = TRUE)
library(palmerpenguins)
library(dplyr)
library(ggplot2)

penguins_clean <- penguins %>% filter(!is.na(body_mass_g))

r_summary <- penguins_clean %>%
  group_by(species) %>%
  summarise(mean_mass = mean(body_mass_g))

r_summary
```

Now hand that R object to Python and do something with it there:

```{python}
import pandas as pd

r_df = r.r_summary
r_df["mean_mass_kg"] = r_df["mean_mass"] / 1000
r_df
```

Read the Python result back into R for the plot:

```{r}
#| label: fig-penguin-mass-combined
#| fig-cap: "Average penguin body mass (kg), computed in Python from an R summary."
combined <- py$r_df

ggplot(combined, aes(x = species, y = mean_mass_kg)) +
  geom_col() +
  labs(x = "Species", y = "Mean body mass (kg)")
```

Gentoo penguins remain the heaviest species on average, whether the
mass is expressed in grams (computed in R) or converted to kilograms
(computed in Python).